---
title: "Shiny App Presentation"
author: "Charles McKay"
date: "3/27/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(plotly)
set.seed(7892)
data(mtcars)
```

## High-Level App Description

- The app predicts a car's 1/4 mile time in seconds
- A linear model based on the "mtcars" dataset generates the prediction
- User inputs are: car weight and horse power
- The "mtcars" dataset and the "new Car" are disleyaed in a Plotly plot
- Shiny App source code can be found here: https://github.com/ckmckay-GH/DDP_APP/tree/master
- This presentation can be found at: http://rpubs.com/ckmckay/262716


## 1/4 Mile Time Prediction Model

```{r cars, echo = TRUE}
mtfit <- lm(qsec ~ wt + hp, data = mtcars)
summary(mtfit)$coef
```

## Plotly Plot 

```{r plot, warnings = FALSE, message=FALSE}
mtcars$model <- rownames(mtcars)
plot_ly(mtcars, x = ~wt, y = ~hp, z = ~qsec, 
        hoverinfo = 'text', text = ~paste(model), name = "mtcars") %>%
        add_markers() %>%
        layout(title = "Car 1/4 Mile Time vs. Weight vs. Horse Power",
                scene = list(
                        title = "Car 1/4 Mile Time vs. Weight vs. Horse Power",
                        xaxis = list(title = 'Weight (lbs 1000s)'),
                        yaxis = list(title = 'Horse Power'),
                        zaxis = list(title = '1/4 Mile Time (seconds)'))) %>%
        add_trace(type = "scatter3d", x = 3.5, y = 200, z = 16.66, 
                text = "New Car", name = 'New Car', mode = 'markers')
```

## App Instructions


- Use sliders to input weight and horse power
- Click on "Click fo Prediction" button
- Predicted 1/4 mile time in seconds will be dislpayed
- 3D plot will update to include orange market for input and predicted car parameters

- Click this link to try the app: https://rollingbay1965.shinyapps.io/ddp_app/
